13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2018-04-10 rules/rules18.tex
Updated important dates.

\begin{description}
\item[May~1] Deadline for new benchmark contributions.
\item[June~1] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~4] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~19] Deadline for final versions of solvers, including
  system descriptions.
\item[June~20] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~22/23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

>>>>

\begin{description}
\item[April~8] Deadline for new benchmark contributions.
\item[May~1] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~10] Deadline for final versions of solvers, including
  system descriptions.
\item[\rem{June~20 TODO update}] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~12/13] SMT Workshop; end of competition, presentation of
  results.
\end{description}
